### 2015-05-11 evaluation.tex
fix

\noindent
\textbf{Race-Checking}\xspace\xspace Table~\ref{tab:stats} presents statistics for all our benchmarks: lines of code (LoC); number of entry point pairs (\#Pairs); number of SMACK memory regions (\#MRs); number of racy pairs that \whoop identified (\#Racy Pairs); number of racy memory regions that \whoop reported (\#Racy MRs); and number of races that \corral discovered (\#Races Found) using a context-switch bound of 2. We did not discover new races with larger context switch bounds. This might mean that these drivers only have races that manifest with at least one or two context-switches, or that \corral run hit its bounds before discovering a deeper race.

>>>>

\noindent
\textbf{Race-Checking}\xspace\xspace Table~\ref{tab:stats} presents statistics for all our benchmarks: lines of code (LoC); number of entry point pairs (\#Pairs); number of SMACK memory regions (\#MRs); number of racy pairs that \whoop identified (\#Racy Pairs); number of racy memory regions that \whoop reported (\#Racy MRs); and number of races that \corral discovered (\#Races Found) using a context-switch bound of 2. We did not discover new races with larger context switch bounds. This might mean that these drivers only have races that manifest with at least one or two context-switches, or that \corral hit its bounds before discovering a deeper race.
